Analysis paper

### 2021-10-11 analysis/analysis.Rmd
update script to run past forecasts
set up trackdown manuscript

df <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]

@@

@@

```{r fig.height=10, fig.width=15}

# pl <- wrap_plots(p_combined, p, widths = c(1, 2)) / p_phases + 
#   plot_layout(guides = "collect") & 
#   plot_annotation(tag_levels = 'A') &
#   theme(legend.position = 'bottom') 
# 
# ggsave("plots/distribution_scores.png", plot = pl, height = 9)

pl_ae <- wrap_plots(p_combined_ae, p_ae, widths = c(1, 2)) / p_phases_wis + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

>>>>

data <- unfiltered_data[model %in% c(regular_models, "Renewal-retrospective", "Convolution-retrospective")]

@@

filtered_data[model %in% regular_models] %>%
  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
  make_table(plotname = "table_mean-late-period")

@@

```{r fig.height=10, fig.width=15}
pl_ae <- wrap_plots(p_combined_ae, p_ae, widths = c(1, 2)) / p_phases_wis + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

filtered_data[model %in% regular_models] %>%
  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
  aggregate_performance(plotname = "aggregate-performance-all-late-period")
